Parenting Observation Experiment 2 Lexical Diversity Analysis

### 2019-07-08 paper/cogsci2019/cogsci2019.Rmd
updated LD Exp 2 analysis

We fit a mixed-effects linear regression predicting TTR as a function of condition, age (scaled and 0-centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4]. 
There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp","beta"]`, t(52.4) = `r e1TTR["conditionexp","zval"]`, *p*<.001). 
There were no significant effects of age, gender, or parent's level of education.
A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`, $\beta=$`r e1MTLD["conditionexp","beta"]`, t(55) = `r e1MTLD["conditionexp","zval"]`, *p*=.001), with no other significant effects.
Figure \ref{fig:e1lex_div} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

>>>>

We fit a mixed-effects linear regression predicting TTR as a function of condition, age (0-centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4]. 
There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp","beta"]`, t(52.4) = `r e1TTR["conditionexp","zval"]`, *p*<.001). 
There were no significant effects of age, gender, or parent's level of education.
A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`, $\beta=$`r e1MTLD["conditionexp","beta"]`, t(55) = `r e1MTLD["conditionexp","zval"]`, *p*=.001), with no other significant effects.
Figure \ref{fig:e1lex_div} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

### 2019-07-08 parenting_obs_e2/Lexical_Diversity_Analysis.Rmd
updated LD Exp 2 analysis

dem <- read.csv("anonymized_demographics_parenting_obs_e2.csv", header=T)
dem$age = as.numeric(as.character(dem$age))
d$age = NULL
dem$X = NULL
d <- d %>% left_join(dem, by=c("sid" = "SID")) %>%
  filter(age <= 2.0)

@@

#Plots

##TTR
```{r echo=FALSE}
ms_lex <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "TTR")

@@

ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
  ylim(0.0, 0.6)+
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("TTR") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
ggsave(file="figs/e2_TTR.pdf", width=3, height=3)
```
## MTLD
```{r echo=FALSE}
ms_lex <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "MTLD")

@@

ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("MTLD") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
ggsave(file="figs/e2_MTLD.pdf", width=3, height=3)
```
## HD-D
```{r echo=FALSE}
ms_lex <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "HDD")

lex_means <- d%>%
  group_by(condition)%>%
  summarise(mean = mean(HDD))

lex_sds <- d%>%
  group_by(condition)%>%
  summarise(sd = sd(HDD))

ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("HD-D") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few()
ggsave(file="figs/e2_HDD.pdf", width=3, height=3)
```
##Word Tokens
```{r echo=FALSE}
ms_tok <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "tokens")

@@

##Word Types
```{r echo=FALSE}
ms_type <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "types")

@@

##Sentence Length
```{r echo=FALSE}
ms_length <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "len_sentence")

@@

###Sentence Length by videos

@@

###Sentence Length by age
(Maybe do a scatterplot with continuous age)

```{r echo=FALSE}
ms_length <- d %>%
  group_by(age) %>%
  multi_boot_standard(col = "len_sentence")

ms_length$age <- factor(ms_length$age,
levels = c("1", "2"),
labels = c("12-18", "18-24"))

ggplot(ms_length, aes(x = age, y = mean, fill = age)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Age (months)") + 
  ylab("Average Sentence Length") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

@@

#Conclusions
In McCarthy-Jarvis2010 paper, MTLD and HD-D has a correlation of r = .800; 
MTLD and TTR r =.322;
HD-D and TTR r = -.051 (N = 1584). 
In our results, MTLD and HD-D have the highest correlation (r = .714). Meanwhile, MTLD and TTR has r = .270, a bit lower than what M-J2010 reported. TTR and HDD are also modestly correlated (r = .426)

>>>>

dem <- read.csv("anonymized_demographics_parenting_obs_e2.csv", header=T)
dem$age = as.numeric(as.character(dem$age))
d$age = NULL
dem$X = NULL
d <- d %>% left_join(dem, by=c("sid" = "SID")) %>%
  filter(age <= 2.0 & age>=1.0)

@@

# Plots

## TTR

```{r echo=FALSE}
ms_lex <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "TTR")

@@

ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
  ylim(0.0, 0.6)+
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("TTR") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
ggsave(file="figs/e2_TTR.pdf", width=3, height=3)
```

## MTLD

```{r echo=FALSE}
ms_lex <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "MTLD")

@@

ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("MTLD") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
ggsave(file="figs/e2_MTLD.pdf", width=3, height=3)
```

## Word Tokens

```{r echo=FALSE}
ms_tok <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "tokens")

@@

## Word Types

```{r echo=FALSE}
ms_type <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "types")

@@

## Sentence Length

```{r echo=FALSE}
ms_length <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "len_sentence")

@@

### Sentence Length by Video

@@

### Sentence Length by age
(Maybe do a scatterplot with continuous age)

```{r echo=FALSE}
ac <- d %>% filter(!is.na(age) & !is.na(condition))
ggplot(ac, aes(x = age, y = len_sentence, group=condition, colour = condition)) +
  geom_point(alpha=.7) + geom_smooth(method='lm') + 
  xlab("Age (years)") + ylab("Mean Sentence Length") +
  langcog::scale_colour_solarized() +
  ggthemes::theme_few() 
```

@@

# Conclusions

In McCarthy-Jarvis2010 paper, MTLD and HD-D has a correlation of r = .800; MTLD and TTR r =.322; HD-D and TTR r = -.051 (N = 1584). 
In our results, MTLD and HD-D have the highest correlation (r = .710). Meanwhile, MTLD and TTR has r = .287, a bit lower than what M-J2010 reported. TTR and HDD are also modestly correlated (r = .444).
